
\begin{center}
\section*{\Huge\textit{Preface}}
\end{center}
\
%\addcontentsline{toc}{chapter}{Preface}
$\\[0.5cm]$

This thesis marks the end of two Master's degrees in Informatics at the Norwegian University of Science and Technology (NTNU). The thesis is a joint project between two students in the Artificial Intelligence and Software Engineering fields respectively. The project duration was from August 2016 to June 2017. A main motivation for us to undertake this project was to make the process of applying for an exchange program both easier and more accessible. Therefore, it was very rewarding for us to get positive results from this research project. We hope our project will contribute to more exchange students from NTNU in the future, and that it may increase the interest for further work on the subject.

We would like to thank our supervisor, Associate Prof. Rune Sætre, for the useful guidance, encouragement, and feedback he has provided us with throughout the year and Assisting Prof. Terje Rydland, for co-supervising the project and participating in interviews. We would also like to thank all the staff at the NTNU Department of Computer Science who assisted us in the process. In particular, we would like to thank Associate Prof. Kerstin Bach for assisting us with everything regarding CBR and myCBR and to Prof. Agnar Aamodt for helping us validate our initial project idea.    Furthermore, we would like to thank the students who participated in usability tests during the development process and those that used their time to answer our questionnaires. Finally, we would like to thank our family and friends for the continuous support and encouragement.
\\\\
\textit{Lars Liverød Andersen} \& \textit{Truls Mørk Pettersen}

Trondheim, 03.06.2017


\cleardoublepage