\chapter{Installation Guide}\label{app:installation_guide}
This guide shows all steps necessary to install and run Utsida locally. The guide is made for Ubuntu 16.04, which is the operative system the Utsida was developed to run on.

\section*{Prerequisites}
The following sections shows commands which downloads the necessary programs to run this project. Skip the programs you already have installed.

\subsection*{Install Java 8}
\begin{minted}{python}
sudo add-apt-repository ppa:webupd8team/java
sudo apt-get update
sudo apt-get install oracle-java8-installer
\end{minted}

\subsection*{Install Python3 and Pip3}
\begin{minted}{python}
sudo apt-get install python3                                       
sudo apt-get install python3-pip   
\end{minted}

\subsection*{Install Git}
\begin{minted}{python}
sudo apt-get install git   
\end{minted}

\section*{Download the Git Repositories}
The following commands downloads the two necessary Git repositories for this project. The first being Utsida's web application, and the second being the MyCBR project.

\begin{minted}{python}
git clone https://github.com/IT3901-Master/utsida.git              
git clone https://github.com/IT3901-Master/mycbr-deployment.git    
\end{minted}


\section*{Setup and Run}
The following commands will install all necessary packages to run the project, initiate all required data, and run it. First, move to the root directory of the utsida project, then run the following commands.

\begin{minted}{python}
sudo pip3 install -r requirements.txt
make initiate
make lrun 
\end{minted}

Open a new terminal or tab, and move to the directory of the mycbr-deployment project. Then run the following command.

\begin{minted}{python}
make run
\end{minted}

